`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-03-05 paper/paper.qmd
add a couple more references, and fix affiliations to render

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - affiliation: 1
    name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
  - affiliation: 1
    name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
  - affiliation: 1,3
    name: Aarathy Babu
    orcid: 
  - affiliation: 1
    name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
  - affiliation: 1,2
    name: Nick Golding
    orcid: 0000-0001-8916-5570
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
date: today
bibliography: paper.bib
---

@@

This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling].

>>>>

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    corresponding: true
    affiliation: "1"
  - name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
    affiliation: "1"
  - name: Aarathy Babu
    orcid: 0000-0002-6982-5989
    affiliation: "1,3"
  - name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
    affiliation: "1"
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: "1,2"
affiliations:
  - index: 1
    name: The Kids Research Institute Australia, WA, Australia
  - index: 2
    name:  University of Western Australia, WA, Australia
  - index: 3
    name: Monash University, VIC, Australia
date: today
bibliography: paper.bib
---

@@

This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].
